

\documentclass{article}
% Template-specific packages

\usepackage{graphicx} % Required for including images
\usepackage[hidelinks]{hyperref}
\usepackage{longtable}
\usepackage{epstopdf}
\usepackage{fullpage,enumitem,amsmath,amssymb,graphicx}
\usepackage{tikz}
\usepackage{pdfpages}
\usepackage{amsmath, amsthm}
\usepackage{fancyhdr}
\usepackage{siunitx}
\usepackage{mathtools}
\usepackage{mathrsfs}
\pagestyle{fancy}
\fancyhead[R]{\rightmark}
\fancyhead[L]{Ali BaniAsad 401209244}
\setlength{\headheight}{10pt}
\setlength{\headsep}{0.2in}
\usepackage{titling}
\usepackage{float}
\newcommand\Tstrut{\rule{0pt}{2.6ex}}         % = `top' strut
\newcommand\Bstrut{\rule[-0.9ex]{0pt}{0pt}}   % = `bottom' strut
%----------------------------------------------------------------------------------------
%	ASSIGNMENT INFORMATION
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
\usepackage{graphicx}
\title{Home Work \#1}
\author{Ali BaniAsad 401209244}

\begin{document}
	\maketitle
	\section*{Dead Reckoning Devices}
\begin{enumerate}
    \item \textbf{Inertial Measurement Unit (IMU):} A sensor package that typically includes accelerometers and gyroscopes. IMUs measure changes in velocity and orientation to estimate position.
    
   
    \item \textbf{Odometer:} A device that measures the distance traveled by a vehicle by counting wheel revolutions.
    
    \item \textbf{Tachometer:} Measures the rotation speed of a vehicle's wheels or other rotating components, aiding in speed and distance calculations.
    
    \item \textbf{Wheel Encoders:} Optical or magnetic sensors attached to a wheel to measure wheel rotation, used in robotics and navigation systems.
    
    \item \textbf{Stride Sensors:} Devices that measure a person's stride length and cadence, often used in pedestrian dead reckoning systems.
    
    \item \textbf{Fiber Optic Gyroscopes (FOGs):} High-precision gyroscopes based on the interference of light traveling through optical fibers.
    
    \item \textbf{Ring Laser Gyroscopes (RLGs):} High-precision gyroscopes that use laser beams in a closed-loop configuration to detect rotation.
\end{enumerate}

\section*{Fixed Positioning Devices}
\begin{enumerate}
    \item \textbf{Global Positioning System (GPS):} A satellite-based navigation system that provides accurate position, velocity, and time information worldwide.
    
    \item \textbf{Galileo Positioning System:} The European global navigation satellite system, similar to GPS, offering global coverage.
    
    \item \textbf{Glonass Navigation System:} The Russian global navigation satellite system, providing global positioning and timing services.
    
    \item \textbf{BeiDou Navigation Satellite System:} China's global satellite navigation system, which offers global and regional services.
    
    \item \textbf{Loran-C:} A terrestrial radio navigation system used for long-range navigation, mainly in coastal areas.
    
    \item \textbf{Quasi-Zenith Satellite System (QZSS):} A Japanese regional satellite navigation system designed to improve GPS accuracy over Japan.
    
    \item \textbf{Indian Regional Navigation Satellite System (IRNSS/NavIC):} India's regional satellite navigation system, primarily covering the Indian subcontinent.
    
    \item \textbf{Differential GPS (DGPS):} Augments GPS by providing correction signals to improve accuracy, often used in maritime and land-based applications.
    
    \item \textbf{Real-Time Kinematic (RTK) GPS:} High-precision GPS technique that uses a reference station to provide centimeter-level accuracy.
    
    \item \textbf{Satellite-Based Augmentation System (SBAS):} Systems like WAAS (USA), EGNOS (Europe), and MSAS (Japan) enhance GPS accuracy through ground-based reference stations.
    
    \item \textbf{Terrestrial Beacon Systems:} Ground-based beacons that transmit signals used for navigation, such as DME (Distance Measuring Equipment) in aviation.
 \item \textbf{Doppler Velocity Log (DVL):} Measures water velocity by analyzing the Doppler shift of acoustic signals reflected off the seabed. Often used in underwater navigation.
    
    \item \textbf{Barometer:} Measures atmospheric pressure changes, which can be used to estimate altitude changes when integrated over time.
    
\end{enumerate}

\section*{Explanation}
Dead reckoning devices rely on internal sensors, vehicle measurements, and motion analysis to estimate position, velocity, and orientation. Fixed positioning methods utilize signals from satellite or ground-based systems to determine precise location, making them less prone to drift and errors compared to dead reckoning.

%	\newpage
%	\tableofcontents
%	\newpage
%	\listoffigures
	% \newpage
	% \listoftables
\end{document}

